### 2017-04-24 Risk analysis/Text/Layout/Layout/chapter3_1Dcase.tex
updated

	The probability distributions for the location of the layer boundaries are treated as priors. Now it is assumed that new observations have been made, providing additional information on the likelihoods of the thicknesses of the two layers. Likelihood functions for reservoir and seal thicknesses are introduced in the form of normal distributions, defined by means and standard deviations. These parameters vary according to nature of the observations made. Using the principle of Bayesian inference as explained in \ref{cha:met}, the model is updated and new posterior distributions for our true reservoir score are attained.

@@

	Different examples with different sets of likelihoods are conducted in the following, so that various possible results can be compared. Each take the layer boundaries defined in  \ref{sec:1D_construction} as priors and use Bayesian inference with data defined below for each example.

@@

	\begin{table}
		\centering
		\begin{tabular}[c]{| l | l | l |}
			\hline
			Risk factor \textit{r} & Shift in Bayes action & Change in expected loss \\ \hline
			0.50 & +~553.67 & -~105.49 \\ 
			0.75 & +~673.40 & -~81.67  \\ 
			1.00 & +~750.05 & -~33.56 \\ 
			1.25 & +~713.19 & +~75.71 \\ 
			1.50 & +~0.00 & +~282.64  \\ 
			\hline
		\end{tabular}
		\caption{Bla}
		\label{tab:update_moderate_tab}
	\end{table}

	Increased certainty about the reservoir thickness is sufficient to shift Bayes actions to higher estimates for all actors, but the most risk-averse one. These shifts are quantified in Table \ref{tab:update_moderate_tab}. According to these numbers, the risk-neutral actor's estimate is increased the most. Expected losses decreased for the risk-neutral and the two risk-friendlier individuals. It is clear that the expected loss was reduced the most for the risk-friendliest actor and it increased most significantly for the most risk-averse actor.

@@

	In this second case, the reservoir thickness likelihood is defined in the same way as before. For the seal, a mean of 50~m with a standard deviation of 20~m is chosen, favoring the likelihood of a reliable seal relative to the threshold of 20~m thickness. This results in the score distribution depicted in \ref{fig:update_goodseal2}. The bulk of the distribution is narrowed on the positive side of estimates. Mean and median are clearly shifted to higher values as well. The "seal failure" peak at -~2000 is significantly. decreased.

@@

	Applying the loss function on this new score distribution results in the realizations of expected loss illustrated in \ref{fig:update_goodseal3}. Bayes actions are shifted clearly to higher estimates and expected losses of these minima are significantly reduced for all actors. This is quantified in \ref{tab:update_goodseal_tab}. According to these values, the risk-neutral to risk-averse individuals seem to profit the most.

@@

	\begin{table}
		\centering
		\begin{tabular}[c]{| l | l | l |}
			\hline
			Risk factor \textit{r} & Shift in Bayes action & Change in expected loss \\ \hline
			0.50 & +~522.95 & -~436.26 \\ 
			0.75 & +~697.73 & -~551.92  \\ 
			1.00 & +~855.57 & -~631.92 \\ 
			1.25 & +~912.43 & -~647.10 \\ 
			1.50 & +~819.26 & -~545.96  \\ 
			\hline
		\end{tabular}
		\caption{Bla}
		\label{tab:update_goodseal_tab}
	\end{table}

@@

	The subsequent score distribution is depicted in \ref{fig:update_smallres2}. It can be seen that while the whole distribution is narrowed, it also is shifted to the left, to lower and negative estimates. Mean and median are almost the same. As seal reliability is practically guaranteed, the peak at -~2000~m vanishes.

	Based on this probability distribution of the reservoir score, Bayes actions are shifted to lower estimates for all actors (\ref{fig:update_smallres3}). In fact, also but the most risk-friendly individual (\textit{r} = 0.5) find their Bayesian estimator to be zero now, i.e. project development is deemed to be too risky to them. Furthermore, the spread of expected loss values around the minima for all actors is diminished (the expected loss values of the Bayes actions are now much closer to each other).

	Quantified changes in the position and the values of the Bayes actions are comparable to the results in example II (there is no shift for risk-averse actors, as they already found their best estimates to be zero). Most notable is the large reduction of expected loss in general (see \ref{tab:update_smallres_tab}).

@@

	\begin{table}
		\centering
		\begin{tabular}[c]{| l | l | l |}
			\hline
			Risk factor \textit{r} & Shift in Bayes action & Change in expected loss \\ \hline
			0.50 & -~498.98 & -~538.08 \\ 
			0.75 & -~346.16 & -~717.83  \\ 
			1.00 & -~176.13 & -~872.02 \\ 
			1.25 & -~0.00 & -~946.04 \\ 
			1.50 & -~0.00 & -~951.57  \\ 
			\hline
		\end{tabular}
		\caption{Bla}
		\label{tab:update_smallres_tab}
	\end{table}

>>>>

	The probability distributions for the location of the layer boundaries are treated as priors. Now it is assumed that new observations have been made, providing additional information on the likelihoods of the thicknesses of the two layers. Likelihood functions for reservoir and seal thicknesses are introduced in the form of normal distributions, defined by means and standard deviations. These parameters vary according to nature of the observations made. Using the principle of Bayesian inference as explained in chapter \ref{cha:met}, the model is updated and new posterior distributions for our true reservoir score are attained.

@@

	Different examples with different sets of likelihoods are conducted in the following, so that various possible results can be compared. Each take the layer boundaries defined in section \ref{sec:1D_construction} about model construction as priors and use Bayesian inference with data defined below for each example.

@@

	%\begin{table}
	%	\centering
	%	\begin{tabular}[c]{| l | l | l |}
	%		\hline
	%		Risk factor \textit{r} & Shift in Bayes action & Change in expected loss \\ \hline
	%		0.50 & +~553.67 & -~105.49 \\ 
	%		0.75 & +~673.40 & -~81.67  \\ 
	%		1.00 & +~750.05 & -~33.56 \\ 
	%		1.25 & +~713.19 & +~75.71 \\ 
	%		1.50 & +~0.00 & +~282.64  \\ 
	%		\hline
	%	\end{tabular}
	%	\caption{Bla}
	%	\label{tab:update_moderate_tab}
	%\end{table}

	Increased certainty about the reservoir thickness is sufficient to shift Bayes actions to higher estimates for all actors, but the most risk-averse one. These shifts are quantified in Table \ref{tab:update_examples_all}. According to these numbers, the risk-neutral actor's estimate is increased the most. Expected losses decreased for the risk-neutral and the two risk-friendlier individuals. It is clear that the expected loss was reduced the most for the risk-friendliest actor and it increased most significantly for the most risk-averse actor.

@@

	In this second case, the reservoir thickness likelihood is defined in the same way as before. For the seal, a mean of 50~m with a standard deviation of 20~m is chosen, favoring the likelihood of a reliable seal relative to the threshold of 20~m thickness. This results in the score distribution depicted in Figure \ref{fig:update_goodseal2}. The bulk of the distribution is narrowed on the positive side of estimates. Mean and median are clearly shifted to higher values as well. The "seal failure" peak at -~2000 is significantly. decreased.

@@

	Applying the loss function on this new score distribution results in the realizations of expected loss illustrated in Figure \ref{fig:update_goodseal3}. Bayes actions are shifted clearly to higher estimates and expected losses of these minima are significantly reduced for all actors. This is quantified in Table \ref{tab:update_examples_all}. According to these values, the risk-neutral to risk-averse individuals seem to profit the most.

@@

	%\begin{table}
	%	\centering
	%	\begin{tabular}[c]{| l | l | l |}
	%		\hline
	%		Risk factor \textit{r} & Shift in Bayes action & Change in expected loss \\ \hline
	%		0.50 & +~522.95 & -~436.26 \\ 
	%		0.75 & +~697.73 & -~551.92  \\ 
	%		1.00 & +~855.57 & -~631.92 \\ 
	%		1.25 & +~912.43 & -~647.10 \\ 
	%		1.50 & +~819.26 & -~545.96  \\ 
	%		\hline
	%	\end{tabular}
	%	\caption{Bla}
	%	\label{tab:update_goodseal_tab}
	%\end{table}

@@

	The subsequent score distribution is depicted in Figure \ref{fig:update_smallres2}. It can be seen that while the whole distribution is narrowed, it also is shifted to the left, to lower and negative estimates. Mean and median are almost the same. As seal reliability is practically guaranteed, the peak at -~2000~m vanishes.

	Based on this probability distribution of the reservoir score, Bayes actions are shifted to lower estimates for all actors (see Figure \ref{fig:update_smallres3}). In fact, also but the most risk-friendly individual (\textit{r} = 0.5) find their Bayesian estimator to be zero now, i.e. project development is deemed to be too risky to them. Furthermore, the spread of expected loss values around the minima for all actors is diminished (the expected loss values of the Bayes actions are now much closer to each other).

	Quantified changes in the position and the values of the Bayes actions are comparable to the results in example II (there is no shift for risk-averse actors, as they already found their best estimates to be zero). Most notable is the large reduction of expected loss in general (see Table \ref{tab:update_examples_all}).

@@

	%\begin{table}
	%	\centering
	%	\begin{tabular}[c]{| l | l | l |}
	%		\hline
	%		Risk factor \textit{r} & Shift in Bayes action & Change in expected loss \\ \hline
	%		0.50 & -~498.98 & -~538.08 \\ 
	%		0.75 & -~346.16 & -~717.83  \\ 
	%		1.00 & -~176.13 & -~872.02 \\ 
	%		1.25 & -~0.00 & -~946.04 \\ 
	%		1.50 & -~0.00 & -~951.57  \\ 
	%		\hline
	%	\end{tabular}
	%	\caption{Bla}
	%	\label{tab:update_smallres_tab}
	%\end{table}

	\begin{table}
		\centering
		\begin{tabular}[c]{| c || l | l || l | l || l | l |}
			\hline
			& Example I & & Example II & & Example III & \\
			\hline
			\hline
			\textit{r} & $\delta$ BA & $\delta$ EL & $\delta$ BA & $\delta$ EL & $\delta$ BA & $\delta$ EL\\ 
			\hline
			0.50 & +~553.67 & -~105.49 & +~522.95 & -~436.26 & -~498.98 & -~538.08 \\ 
			0.75 & +~673.40 & -~81.67 & +~697.73 & -~551.92 & -~346.16 & -~717.83  \\ 
			1.00 & +~750.05 & -~33.56 & +~855.57 & -~631.92 & -~176.13 & -~872.02 \\ 
			1.25 & +~713.19 & +~75.71 & +~912.43 & -~647.10 & -~0.00 & -~946.04 \\ 
			1.50 & +~0.00 & +~282.64 & +~819.26 & -~545.96 & -~0.00 & -~951.57  \\ 
			\hline
		\end{tabular}
		\caption{Bla}
		\label{tab:update_examples_all}
	\end{table}
